Summer 2025 ToDo

### 2025-11-13 Relations/Paper/Well-foundedness.tex
Typo fix

On the other hand, assuming accessibility is $\lnot\lnot$-closed, the other
hypothesis can now be weakened, to only require existence of minimal elements
for $\lnot\lnot$-closed subsets.  This is a significant restriction, which may
be validated in certain cases.  In contrast, the original hypothesis
(postulating minimal elements for ALL predicates)
is generally equivalent to every subset being decidable.
The file \texttt{WFCounters.agda} shows that assuming the full minimality hypothesis $\WFmin$ for the standard strict order on the natural numbers entails decidability of every subset of $\nat$ (which is clearly incompatible with effective semantics), while its restriction $\WFminDNE$ implies
%(and is equivalent to)
that each subset $P$ it \emph{weakly} decidable,
satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ for all $x$.

@@

In \cite{Terese}, the $\WFseqm$ definition is used, as in the classical mathematics textbooks. Constructively, this is not a useful definition, as it does not provide any positive computational content and requires an explicit sequence to be defined.  This definition appears to be strictly weaker than
$\WFseqnn$, asserting that every sequence not-not contains a
non-decreasing index.

>>>>

On the other hand, assuming accessibility is $\lnot\lnot$-closed, the other
hypothesis can now be weakened, to only require existence of minimal elements
for $\lnot\lnot$-closed subsets.  This is a significant restriction, which may
be validated in certain cases.  In contrast, the original hypothesis
(postulating minimal elements for ALL predicates)
is generally equivalent to every subset being decidable.
The file \texttt{WFCounters.agda} shows that assuming the full minimality hypothesis $\WFmin$ for the standard strict order on the natural numbers entails decidability of every subset of $\nat$ (which is clearly incompatible with effective semantics), while its restriction $\WFminDNE$ implies
%(and is equivalent to)
that each subset $P$ is \emph{weakly} decidable,
satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ for all $x$.

@@

In \terese, the $\WFseqm$ definition is used, as in the classical mathematics textbooks. Constructively, this is not a useful definition, as it does not provide any positive computational content and requires an explicit sequence to be defined.  This definition appears to be strictly weaker than
$\WFseqnn$, asserting that every sequence not-not contains a
non-decreasing index.
